---
title: "Event Data"
author: "Luke Julian"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    df_print: tibble
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.height = 4)
setwd("C:/users/luke/Personal_Projects/Soccer/stats_bomb/")
source("StatsBombFun.R")
library(ggplot2)
library(ggrepel)
```

## Intorduction

Data courtesy of *StatsBomb*. Data used for this document is from the 2018 and 2022 Men's World Cups, the 2019 Women's world Cup, and the 2022 Women's Euros.

```{r Read In Event Data, results='hide', message=FALSE, warning=FALSE}
events.wc.22 <- allclean(get.competitionEvents(43,106))
events.wc.18 <- allclean(get.competitionEvents(43,3))
events.wwc.19 <- allclean(get.competitionEvents(72,30))
events.weuro.22 <- allclean(get.competitionEvents(53,106))
```
```{r Load event files}
# events.wc.18 <- read.csv("Data/Events/wc22.csv")
# events.wc.22 <- read.csv("Data/Events/wc18.csv")
# events.wwc.19 <- read.csv("Data/Events/wwc19.csv")
# events.weuro.22 <- read.csv("Data/Events/weuro22.csv")
```
```{r, message=FALSE, warning=FALSE}
wc.18.matches <- get.match_info(events.wc.18)
wc.22.matches <- get.match_info(events.wc.22)
wwc.19.matches <- get.match_info(events.wwc.19)
weuro.22.matches <- get.match_info(events.weuro.22)
```

Try to run only once:

```{r Create Progressive Stats}
# carry.wc.18 <- get.progressive(events.wc.18,"Carry")
# pPass.wc.18 <- get.progressive(events.wc.18,"Pass")
# 
# carry.wc.22 <- get.progressive(events.wc.22,"Carry")
# pPass.wc.22 <- get.progressive(events.wc.22,"Pass")
# 
# carry.wwc.19 <- get.progressive(events.wwc.19,"Carry")
# pPass.wwc.19 <- get.progressive(events.wwc.19,"Pass")
# 
# carry.weuro.22 <- get.progressive(events.weuro.22,"Carry")
# pPass.weuro.22 <- get.progressive(events.weuro.22,"Pass")
```
```{r Load Progressive Stats}
carry.wc.18 <- read.csv("Data/Prog/wc18_carry")
pPass.wc.18 <- read.csv("Data/Prog/wc18_pPass")

carry.wc.22 <- read.csv("Data/Prog/wc22_carry")
pPass.wc.22 <- read.csv("Data/Prog/wc22_pPass")

carry.wwc.19 <- read.csv("Data/Prog/wwc19_carry")
pPass.wwc.19 <- read.csv("Data/Prog/wwc19_pPass")

carry.weuro.22 <- read.csv("Data/Prog/weuro22_carry")
pPass.weuro.22 <- read.csv("Data/Prog/weuro22_pPass")
```

All player stats should be normalized to per 90 minute. Players that have played less than 180 total minutes in the World Cup are excluded from rate statistics.

```{r message=FALSE, warning=FALSE}
wc.22.ind <- compile.individualStats(events.wc.22,carry.wc.22,pPass.wc.22)
wc.18.ind <- compile.individualStats(events.wc.18,carry.wc.18,pPass.wc.18)


wwc.19.ind <- compile.individualStats(events.wwc.19,carry.wwc.19,pPass.wwc.19)
weuro.22.ind <- compile.individualStats(events.weuro.22,carry.weuro.22,pPass.weuro.22)
```

```{r message=FALSE, warning=FALSE}
am.wc.22 <- get.attacking_ballMovement_stats.ind(events.wc.22) %>% filter(player.id %in% wc.22.ind$player.id)
wc.22.ind <- merge(wc.22.ind, am.wc.22, by=c("player.id","player.name","team.name"))
am.wc.18 <- get.attacking_ballMovement_stats.ind(events.wc.18) %>% filter(player.id %in% wc.18.ind$player.id)
wc.18.ind <- merge(wc.18.ind, am.wc.18, by=c("player.id","player.name","team.name"))

am.wwc.19 <- get.attacking_ballMovement_stats.ind(events.wwc.19) %>% filter(player.id %in% wwc.19.ind$player.id)
wwc.19.ind <- merge(wwc.19.ind, am.wwc.19, by=c("player.id","player.name","team.name"))
am.weuro.22 <- get.attacking_ballMovement_stats.ind(events.weuro.22) %>% filter(player.id %in% weuro.22.ind$player.id)
weuro.22.ind <- merge(weuro.22.ind, am.weuro.22, by=c("player.id","player.name","team.name"))
```

```{r}
wc.18.ind.90 <- to.per90(wc.18.ind)
wc.22.ind.90 <- to.per90(wc.22.ind)

wwc.19.ind.90 <- to.per90(wwc.19.ind)
weuro.22.ind.90 <- to.per90(weuro.22.ind)
```

```{r, echo=FALSE}
wc.22.ind.90["pos_group.name"] <- ifelse(
  wc.22.ind.90$position.primary %in% get.defense.id(),
  "DF",
  ifelse(
    wc.22.ind.90$position.primary %in% get.midfield.id(),
    "MF",
    ifelse(
      wc.22.ind.90$position.primary %in% get.attack.id(),
      "FW",
      NA
    )
  )
)
wc.22.ind.90 <- wc.22.ind.90 %>% filter(position.primary!=1)

wc.18.ind.90["pos_group.name"] <- ifelse(
  wc.18.ind.90$position.primary %in% get.defense.id(),
  "DF",
  ifelse(
    wc.18.ind.90$position.primary %in% get.midfield.id(),
    "MF",
    ifelse(
      wc.18.ind.90$position.primary %in% get.attack.id(),
      "FW",
      NA
    )
  )
)
wc.18.ind.90 <- wc.18.ind.90 %>% filter(position.primary!=1)

wwc.19.ind.90["pos_group.name"] <- ifelse(
  wwc.19.ind.90$position.primary %in% get.defense.id(),
  "DF",
  ifelse(
    wwc.19.ind.90$position.primary %in% get.midfield.id(),
    "MF",
    ifelse(
      wwc.19.ind.90$position.primary %in% get.attack.id(),
      "FW",
      NA
    )
  )
)
wwc.19.ind.90 <- wwc.19.ind.90 %>% filter(position.primary!=1)

weuro.22.ind.90["pos_group.name"] <- ifelse(
  weuro.22.ind.90$position.primary %in% get.defense.id(),
  "DF",
  ifelse(
    weuro.22.ind.90$position.primary %in% get.midfield.id(),
    "MF",
    ifelse(
      weuro.22.ind.90$position.primary %in% get.attack.id(),
      "FW",
      NA
    )
  )
)
weuro.22.ind.90 <- weuro.22.ind.90 %>% filter(position.primary!=1)
```

# Progressive Play

A progressive action is one that advances the ball 10 yards closer to goal than than to furthest it has been in the last 6 relevant events in the sequence of play, or when the ball in entered into the 18 yard box. The the common actions that can be considered progressive are passes (pP) and carries (pC).

##### Progressive summary of players at the 2022 World Cup

```{r}
summary(wc.22.ind.90 %>% arrange(desc(pC)) %>% select(team.name,pC,pP,X90s))
```

##### Progressive summary of players at the 2018 World Cup

```{r}
summary(wc.18.ind.90 %>% arrange(desc(pC)) %>% select(pC,pP,X90s))
```

### Progression at the 2022 World Cup

```{r fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
mPC <- max(wc.18.ind.90$pC, wc.22.ind.90$pC, wwc.19.ind.90$pC, weuro.22.ind.90$pC)
mPP <- max(wc.18.ind.90$pP, wc.22.ind.90$pP, wwc.19.ind.90$pP, weuro.22.ind.90$pP)

gplt <- ggplot(wc.22.ind.90, 
               aes(y=pC,
                   x=pP,
                   # label=ifelse(
                   #   labBool,
                   #   paste(player.name,team.name,sep='\n'),
                   #   NA
                   #  ), 
                   label=paste(player.name,team.name,sep='\n'),
                   shape=factor(pos_group.name),
                   color=factor(team.name)
                  )
              ) +
  xlim(0, mPP) +
  ylim(0, mPC) +
  geom_point() +
  geom_text_repel(size=2) +
  labs(title = "2022 World Cup") +
  ylab("Progressive-Carries per 90") +
  xlab("Progressive-Passes per 90") +
  scale_colour_discrete(name="Nation") + 
  scale_shape_discrete(name="Postion") +
  guides(fill=guide_legend(ncol=3)) +
  coord_fixed(max(wc.22.ind.90$pP)/max(wc.22.ind.90$pC))
plot(gplt)
```

### Progression at the 2018 World Cup

```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
gplt <- ggplot(wc.18.ind.90, 
               aes(y=pC,
                   x=pP,
                   label=paste(player.name,team.name,sep='\n'),
                   shape=factor(pos_group.name),
                   color=factor(team.name)
                  )
              ) +
  ylim(0, mPC) +
  xlim(0, mPP) +
  geom_point() +
  geom_text_repel(size=2) +
  labs(title = "2018 World Cup") +
  ylab("Progressive-Carries per 90") +
  xlab("Progressive-Passes per 90") +
  scale_colour_discrete(name="Nation") + 
  scale_shape_discrete(name="Postion") +
  coord_fixed(max(wc.18.ind.90$pP)/max(wc.18.ind.90$pC))
plot(gplt)
```

### Progression at the 2019 World Cup

```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
gplt <- ggplot(wwc.19.ind.90, 
               aes(y=pC,
                   x=pP,
                   label=paste(player.name,sub(" Women's", "", team.name),sep='\n'),
                   shape=factor(pos_group.name),
                   color=factor(sub(" Women's", "", team.name))
                  )
              ) +
  ylim(0, mPC) +
  xlim(0, mPP) +
  geom_point() +
  geom_text_repel(size=2) +
  labs(title = "2019 World Cup") +
  ylab("Progressive-Carries per 90") +
  xlab("Progressive-Passes per 90") +
  scale_colour_discrete(name="Nation") + 
  scale_shape_discrete(name="Postion") +
  guides(fill=guide_legend(ncol=2)) +
  coord_fixed(max(wwc.19.ind.90$pP)/max(wwc.19.ind.90$pC))
plot(gplt)
```

### Progression at the 2022 Women's Euros

```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
gplt <- ggplot(weuro.22.ind.90, 
               aes(y=pC,
                   x=pP,
                   label=paste(player.name,sub(" Women's", "", team.name),sep='\n'),
                   shape=factor(pos_group.name),
                   color=factor(sub(" Women's", "", team.name))
                  )
              ) +
  ylim(0, mPC) +
  xlim(0, mPP) +
  geom_point() +
  geom_text_repel(size=2) +
  labs(title = "2022 Women's Euros") +
  ylab("Progressive-Carries per 90") +
  xlab("Progressive-Passes per 90") +
  scale_colour_discrete(name="Nation") + 
  scale_shape_discrete(name="Postion") +
  guides(fill=guide_legend(ncol=2)) +
  coord_fixed(max(weuro.22.ind.90$pP)/max(weuro.22.ind.90$pC))
plot(gplt)
```

Fun little observation: Mapi Leon, the Spanish defender responsible for the most progressive passes and over 5 progressive carries per 90 at Euro22, is one of the exiled players from Jorge Vilda's World Cup squad. While the group of players has dwindled, she is one of the group refusing to play for the national team while Vilda remains its manager.

## Directness

### Team Play

Directness of play can be measured by the speed at which a team progresses the ball. The directness of a sequence play (a sequence being connsecutive attacking actions, such as passes, carries, dribbles, shots) is the progressed distance from the first event in the sequence to the last per second (so divided by the duration of the sequence). The intricacy of team also relates to how direct they play, which is simply the number of passes per sequence. Generally less direct teams pass more, opting from to patiently move the ball backwards and side to side.

```{r echo=F, fig.height=4, fig.width=7.5, message=FALSE, warning=FALSE}
plot.directness.competition(events.wc.22, title = "Directness of Teams at the 2022 World Cup")
```

```{r echo=F, fig.height=4, fig.width=7.5, message=FALSE, warning=FALSE}
plot.directness.competition(events.wc.18, title = "Directness of Teams at the 2018 World Cup")
```

```{r echo=F, fig.height=4, fig.width=7.5, message=FALSE, warning=FALSE}
plot.directness.competition(events.wwc.19, title = "Directness of Teams at the 2019 World Cup")
```

```{r echo=F, fig.height=4, fig.width=7.5, message=FALSE, warning=FALSE}
plot.directness.competition(events.weuro.22, title = "Directness of Teams at the 2022 Women's Euros")
```

### Attacks

A direct attack is a possession starting in the defensive half in which over half the offensive actions move the ball closer to the goal.

```{r fig.height=4, message=FALSE, warning=FALSE}
da.wc.22 <- get.directAttacks(events.wc.22) %>%
  group_by(team.id,team.name) %>%
  summarise(
    matches = length(unique(match_id)),
    direct.attacks = length(which(directAttack)),
    direct.goals = length(which(directAttack & goal)),
    direct.attacks.percent = length(which(directAttack)) / length(directAttack),
    direct.goals.percent = length(which(directAttack & goal)) / 
      length(which(goal))
  )

gplt <- ggplot(da.wc.22, 
               aes(
                 x=direct.attacks/matches, y=direct.attacks.percent, label=team.name
               )) +
  geom_point() +
  geom_text_repel(color="white") +
  xlab("Direct Attacks per Match") + ylab("% of Shots from Direct Attacks") +
  labs(title = "2022 World Cup") + 
    geom_hline(aes(yintercept=mean(direct.attacks.percent)), alpha=0.35, color="snow2") +
  geom_vline(aes(xintercept=mean(direct.attacks/matches)), alpha=0.35, color="snow2") +
  theme_dark()
plot(gplt)
```

```{r fig.height=4, message=FALSE, warning=FALSE}
da.wc.18 <- get.directAttacks(events.wc.18) %>%
  group_by(team.id,team.name) %>%
  summarise(
    matches = length(unique(match_id)),
    direct.attacks = length(which(directAttack)),
    direct.goals = length(which(directAttack & goal)),
    direct.attacks.percent = length(which(directAttack)) / length(directAttack),
    direct.goals.percent = length(which(directAttack & goal)) / 
      length(which(goal))
  )

gplt <- ggplot(da.wc.18, 
               aes(
                 x=direct.attacks/matches, y=direct.attacks.percent, label=team.name
               )) +
  geom_point() +
  geom_text_repel(color="white") +
  xlab("Direct Attacks per Match") + ylab("% of Shots from Direct Attacks") +
  labs(title = "2018 World Cup") + 
  geom_hline(aes(yintercept=mean(direct.attacks.percent)), alpha=0.35, color="snow2") +
  geom_vline(aes(xintercept=mean(direct.attacks/matches)), alpha=0.35, color="snow2") +
  theme_dark()
plot(gplt)
```

```{r fig.height=4, message=FALSE, warning=FALSE}
da.wwc.19 <- get.directAttacks(events.wwc.19) %>%
  group_by(team.id,team.name) %>%
  summarise(
    matches = length(unique(match_id)),
    direct.attacks = length(which(directAttack)),
    direct.goals = length(which(directAttack & goal)),
    direct.attacks.percent = length(which(directAttack)) / length(directAttack),
    direct.goals.percent = length(which(directAttack & goal)) / 
      length(which(goal))
  )

gplt <- ggplot(da.wwc.19, 
               aes(
                 x=direct.attacks/matches, y=direct.attacks.percent, label=sub(" Women's", "", team.name)
               )) +
  geom_point() +
  geom_text_repel(color="white") +
  xlab("Direct Attacks per Match") + ylab("% of Shots from Direct Attacks") +
  labs(title = "2019 World Cup") + 
  geom_hline(aes(yintercept=mean(direct.attacks.percent)), alpha=0.35, color="snow2") +
  geom_vline(aes(xintercept=mean(direct.attacks/matches)), alpha=0.35, color="snow2") +
  theme_dark()
plot(gplt)
```

```{r fig.height=4, message=FALSE, warning=FALSE}
da.weuro.22 <- get.directAttacks(events.weuro.22) %>%
  group_by(team.id,team.name) %>%
  summarise(
    matches = length(unique(match_id)),
    direct.attacks = length(which(directAttack)),
    direct.goals = length(which(directAttack & goal)),
    direct.attacks.percent = length(which(directAttack)) / length(directAttack),
    direct.goals.percent = length(which(directAttack & goal)) / 
      length(which(goal))
  )

gplt <- ggplot(da.weuro.22, 
               aes(
                 x=direct.attacks/matches, y=direct.attacks.percent, label=sub(" Women's", "", team.name)
               )) +
  geom_point() +
  geom_text_repel(color="white") +
  xlab("Direct Attacks per Match") + ylab("% of Shots from Direct Attacks") +
  labs(title = "2022 Euros") + 
  geom_hline(aes(yintercept=mean(direct.attacks.percent)), alpha=0.35, color="snow2") +
  geom_vline(aes(xintercept=mean(direct.attacks/matches)), alpha=0.35, color="snow2") +
  theme_dark()
plot(gplt)
```

### Forward Movement

#### 2022 World Cup
```{r}
gplt <- ggplot(wc.22.ind.90 %>% filter(pos_group.name!="DF"), aes(x=pass.attacking.percent, y=carry.attacking.percent, label=player.name, shape=factor(pos_group.name), color=pass.attacking / (pass.attacking+carry.attacking))) +
  geom_point() +
  geom_text_repel() +
  scale_color_continuous(name="Pass vs Carry") + 
  scale_shape_discrete(name="Postion")
plot(gplt)
```

#### 2018 World Cup
```{r}
gplt <- ggplot(wc.18.ind.90 %>% filter(pos_group.name!="DF"), aes(x=pass.attacking.percent, y=carry.attacking.percent, label=player.name, shape=factor(pos_group.name), color=pass.attacking / (pass.attacking+carry.attacking))) +
  geom_point() +
  geom_text_repel() +
  scale_color_continuous(name="Pass vs Carry") + 
  scale_shape_discrete(name="Postion")
plot(gplt)
```

#### 2019 World Cup

```{r}
gplt <- ggplot(wwc.19.ind.90 %>% filter(pos_group.name!="DF"), aes(x=pass.attacking.percent, y=carry.attacking.percent, label=player.name, shape=factor(pos_group.name), color=pass.attacking / (pass.attacking+carry.attacking))) +
  geom_point() +
  geom_text_repel() +
  scale_color_continuous(name="Pass vs Carry") + 
  scale_shape_discrete(name="Postion")
plot(gplt)
```

#### 2022 Euros

```{r}
gplt <- ggplot(weuro.22.ind.90 %>% filter(pos_group.name!="DF"), aes(x=pass.attacking.percent, y=carry.attacking.percent, label=player.name, shape=factor(pos_group.name), color=pass.attacking / (pass.attacking+carry.attacking))) +
  geom_point() +
  geom_text_repel() +
  scale_color_continuous(name="Pass vs Carry") + 
  scale_shape_discrete(name="Postion")
plot(gplt)
```


# Passing Networks

Passing networks a fairly intuitive football-data visualization. The points/nodes represent each player on a given team, and the line/path connections between represent passes between two players. Nodes are placed at the average location that a given player passes the ball. Passes are normalized to per 90 minute rate. Connections are made when the first player passes to the second at least five times per 90. The number of passes per 90 scales the sizes of the nodes and lines. The network only represents the passes made by the first eleven, and it stops when the first sub is made for the team.

### 2022 World Cup Final

```{r, echo=FALSE, fig.height=6, fig.width=4, message=FALSE, warning=FALSE}
final.22.id <- max(wc.22.matches$match_id)
tms <- unique(events.wc.22 %>% filter(match_id==final.22.id))$team.id
plot.passingNetwork(events.wc.22,final.22.id,tms[1])
```

The passing networks above can tell the story of a match (at least part of it) and the roles of certain players. First looking at Argentina's network, nearly every players has at least three line connected to them; this shows that the team was strongly connected by passing and passing well. Additionally we can see that on a simple level, Argentina setup in a 4-3-3 with the fullbacks pushing up slightly further and Mac Allister playing more advanced than his midfield partners. More interestingly, there is an obvious difference in how their outside forwards play. Di Maria on the left is pushed high and wide, reflecting how his play focused around taking on defenders in wide-attacking areas to create chances, such as winning a penalty for the first goal. On the right is Messi. Throughout Messi's entire career, his positioning has been basically the same with some variations on it: He plays toward the right, and comes more centrally and deeper to get the ball. His positioning for Argentina follows this rule, with his average passing position being nearly as deep as the highest midfielder, and his width being on the border of the central area and right half-space.\

```{r, echo=FALSE, fig.height=6, fig.width=4, message=FALSE, warning=FALSE}
plot.passingNetwork(events.wc.22,final.22.id,tms[2])
```

France's passing network tells a completely different story. As aside from the defense and the outside-backs to the wingers, there is very little connecting. Perhaps most concerningly, the midfield has almost no connections at all. Tchouameni has no connections with his defense, showing him completely unable to connect the defense and attack. Meanwhile, Greizman is on island high up the pitch. The network also shows only one link to the team's centerforward (Giroud), which is a faint link from his goalkeeper. If the lack of passing and connectedness doesn't show that France struggled to generate attacks, the fact that their striker couldn't get the ball should.\
Watching the match backs up these conclusions, with France looking so lost that they made substitutions before halftime, and Argentina completely controlling the game until Di Maria's departure in the 62 minute. What happened after that was a different story, but each network cut off before the game flipped.

### 2018 World Cup Final

```{r, echo=FALSE, fig.height=6, fig.width=4, message=FALSE, warning=FALSE}
final.18.id <- max(wc.18.matches$match_id)
tms <- unique((events.wc.18 %>% filter(match_id==final.18.id))$team.id)
plot.passingNetwork(events.wc.18,final.18.id,tms[1])
```

```{r, echo=FALSE, fig.height=6, fig.width=4, message=FALSE, warning=FALSE}
final.18.id <- max(wc.18.matches$match_id)
plot.passingNetwork(events.wc.18,final.18.id,tms[2])
```

# Defense
## Ball Recoveries
### World Cup 2018
Here are some ball recovery maps from the 2018 world cup. These are 4 of the top 5 outfield players in totals in that category. Which is a great excuse to behold the beauty of an N'Golo Kante Ball Recovery Map.
```{r, echo=FALSE, fig.height=5, fig.width=3.3, message=FALSE, warning=FALSE, paged.print=TRUE}
events.br <- events.wc.18 %>% filter(type.id==2 & is.na(ball_recovery.recovery_failure))
events.br["unit"] <- rep(1, each=nrow(events.br))
br.plr.count <- events.br %>% group_by(player.id, player.name, team.name) %>% 
  summarise(total_br=sum(unit)) %>% 
  arrange(desc(total_br))
br.plr.count
plot.ball_recoveries(events.wc.18, 3961)
plot.ball_recoveries(events.wc.18, 5463)
plot.ball_recoveries(events.wc.18, 3089)
plot.ball_recoveries(events.wc.18, 5485)
```

### PPDA
PPDA (Passes Per Defensive Action) is probably the leading statistic in measuring a teams the intensity and effectiveness of a teams high press. Looking only at the attcking 60% of the pitch, PPDA is calculated by dividing the total passes of the opposition by the total number of defensive actions (tackle attempts, interceptions, and fouls committed) perform. Lower the PPDA that teams emphasize pressuring there opposition with urgency high up the pitch. Higher PPDA shows that a team is content sitting back and on letting the opposition come to them.

```{r fig.height=4}
ppda.all <- c()
for (tm.id in unique(events.weuro.22$team.id)) {ppda.all<-c(ppda.all,get.PPDA(events.weuro.22,tm.id))}
ppda.teams <- merge(
  unique(events.weuro.22[,c("team.name","team.id")]),
  data.frame(team.id=unique(events.weuro.22$team.id), ppda=ppda.all),
  by="team.id"
) %>% arrange(ppda)
gplt <- ggplot(ppda.teams, aes(y=ppda, x=1:length(ppda.all), label=sub(" Women's", "", team.name))) +
  geom_col() +
  geom_text(angle=90, hjust="left", y=0.1, color="white") +
  theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  ) +
  labs(title = "PPDA at Euro22")
plot(gplt)
```

```{r echo=FALSE, fig.height=4}
ppda.all <- c()
for (tm.id in unique(events.wwc.19$team.id)) {ppda.all<-c(ppda.all,get.PPDA(events.wwc.19,tm.id))}
ppda.teams <- merge(
  unique(events.wwc.19[,c("team.name","team.id")]),
  data.frame(team.id=unique(events.wwc.19$team.id), ppda=ppda.all),
  by="team.id"
) %>% arrange(ppda)
gplt <- ggplot(ppda.teams, aes(y=ppda, x=1:length(ppda.all), label=sub(" Women's", "", team.name))) +
  geom_col() +
  geom_text(angle=90, hjust="left", y=0.1, color="white") +
  theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  ) +
  labs(title = "PPDA at World Cup 2019")
plot(gplt)
```

```{r echo=FALSE, fig.height=4}
ppda.all <- c()
for (tm.id in unique(events.wc.22$team.id)) {ppda.all<-c(ppda.all,get.PPDA(events.wc.22,tm.id))}
ppda.teams <- merge(
  unique(events.wc.22[,c("team.name","team.id")]),
  data.frame(team.id=unique(events.wc.22$team.id), ppda=ppda.all),
  by="team.id"
) %>% arrange(ppda)
gplt <- ggplot(ppda.teams, aes(y=ppda, x=1:length(ppda.all), label=team.name)) +
  geom_col() +
  geom_text(angle=90, hjust="left", y=0.1, color="white") +
  theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  ) +
  labs(title = "PPDA at World Cup 2022")
plot(gplt)
```

```{r echo=FALSE, fig.height=4}
ppda.all <- c()
for (tm.id in unique(events.wc.18$team.id)) {ppda.all<-c(ppda.all,get.PPDA(events.wc.18,tm.id))}
ppda.teams <- merge(
  unique(events.wc.18[,c("team.name","team.id")]),
  data.frame(team.id=unique(events.wc.18$team.id), ppda=ppda.all),
  by="team.id"
) %>% arrange(ppda)
gplt <- ggplot(ppda.teams, aes(y=ppda, x=1:length(ppda.all), label=team.name)) +
  geom_col() +
  geom_text(angle=90, hjust="left", y=0.1, color="white") +
  theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  ) +
  labs(title = "PPDA at World Cup 2018")
plot(gplt)
```

In all these tournaments, two nations consistently ranked high in PPDA: Spain and Germany. For Spain, an underrated point of their famous style, Tiki-Taka, is to immediately win the ball back once losing it (known as counterpressing), pressing the opponent high up the pitch to win the ball in attacking positions. For Germany, the style of gegenpressing is perhaps their most influential export of the last decade. The entire system revolves around getting high up the pitch and intensely pressing to win the ball in advantagous positions. One of the best managers of this era, German Jurgen Klopp said, "No playmaker in the world can be as good as a good counter-pressing situation."